\section{SELECTED CONFERENCE ABSTRACTS}

More comprehensive lists of abstracts are available on the \href{https://ui.adsabs.harvard.edu/search/q=author%3A%22Edwards%2C%20Graham%20Harper%22}{Astrophysical Data System} and \href{https://scholar.google.com/citations?user=KHLOvgcAAAAJ&hl=en}{Google Scholar}.

\hfill* mentored student author

\begin{etaremune} [itemsep=4pt, leftmargin=3ex]
  
  \item E.R.~Garrett*, L.P.~Moreton*, \ghedwards, G.~Piccione. 2025. [Poster]: Modern problems require ancient lakes: the chronology and chemistry of Glacial Lake Hitchcock. \textit{Geological Society of America: Connects 2025}, San Antonio, TX, U.S.A. Abstract No.~9078.
  
  \item \ghedwards, G.~Piccione, L.~Moreton*, E.R.~Garrett*, D.S.~Jones, C.~Danhof. 2025. [Oral]: A hydrologically and biologically complex proglacial lake system at the margins of the collapsing Laurentide Ice Sheet. \textit{Geological Society of America: Connects 2025}, San Antonio, TX, U.S.A. Abstract No.~\href{https://gsameetings.secure-platform.com/connects25/solicitations/103002/sessiongallery/schedule/items/95040/application/8850}{8850}.

  \item \ghedwards, C.B.~Keller, E.R.~Newton, R.~Rampalli*. 2025. [Poster]: Statistical cosmochemistry: gaining new perspectives from old (and new) data. \textit{56\textsuperscript{th} Lunar \& Planetary Science Conference}, Woodlands, TX, U.S.A. Abstract No.~\href{https://www.hou.usra.edu/meetings/lpsc2025/pdf/2505.pdf}{2505}.

  \item \ghedwards, C.B.~Keller, E.R.~Newton, C.~Stewart*. 2023. [Talk]: Disk-driven migration of Jupiter: support from meteorite thermochronology. \textit{Goldschmidt Conf.}, Lyon, FR. \doi{10.7185/gold2023.18450}

  \item \ghedwards, G.~Piccione, M.~Gomez. 2022. [Poster]: Comparing in-person and virtual modes of a 4-year museum-based geoscience outreach program. \textit{Earth Educators' Rendezvous 2022}, Minneapolis, MN, U.S.A.

  \item \ghedwards, T.~Blackburn, G.~Piccione, S.~Tulaczyk, G.H.~Miller, C.~Sikes*. 2020. [Talk]: Baffin Island subglacial precipitates record subglacial melting beneath the northern Laurentide Ice Sheet concurrent with Heinrich events. \textit{American Geophysical Union Fall Meeting}, New Orleans, LA, U.S.A.

  \item C.T.~Varah-Sikes*, \ghedwards, T.~Blackburn. 2020. [Poster]: Thermal histories in Type 7 ordinary chondrites: interpreting residence in parent body using petrologic observation and Pb-Pb phosphate thermochronology. \textit{Geological Society of America Annual Scientific Meeting}, Virtual.

  \item  \ghedwards, T.~Blackburn, S.~Tulaczyk, G.G.~Piccione. 2019. [Poster]: U-Series isotopics constrain timescale of bedrock comminution and glacial incision in Taylor Valley, Antarctica. \textit{Goldschmidt Conference}, Barcelona, ES.


  \item  \ghedwards, T.~Blackburn, C.M.O’D.~Alexander. 2017. [Talk]: Accretion and disruption histories of the ordinary chondrite parent bodies. \textit{80\textsuperscript{th} Annual Meeting of the Meteoritical Society}, Santa Fe, NM, U.S.A.

  \item \ghedwards. 2014. [Poster]: Geochemical and stratigraphic analysis of the Linnévatnet sediment record: a provenance study of Late Holocene cirque glacier activity in Linnédalen, Spitsbergen, Svalbard. \textit{44\textsuperscript{th} International Arctic Workshop}, Boulder, CO, U.S.A.
\end{etaremune}


%%%%%%
%% Tomb of Abstracts
%%%%%%
 
%\item \ghedwards, C.B. Keller,  E.R. Newton, C. Stewart. 2023. [iPoster]: Constraining the timescales of giant planet migration from the meteorite record. \textit{241\textsuperscript{st} American Astronomical Society Meeting}, Seattle, WA, U.S.A.

%\item \ghedwards, T. Blackburn, S. Tulaczyk, G.G. Piccione. 2019. [Poster]: U-series isotopics of silts from Taylor Valley, Antarctica: Applying comminution dating methods on polar desert tills and implications for the timeframe of valley incision. \textit{American Geophysical Union Fall Meeting}, San Francisco, CA, U.S.A.

%  \item  \ghedwards, T.~Blackburn, G.G.~Piccione. 2018. [Talk]: Cooling and disruption of the LL chondrite parent body. \textit{Lunar and Small Bodies Graduate Forum (LunGradCon)}, Mountain View, CA, U.S.A.

%   \item \ghedwards, T.~Blackburn, K.V.~Smit. 2017. [Poster]: Timescales of crustal cooling of the Superior Craton near Attawapiskat, Ontario, Canada, and implications for extent of Keweenawan plume heating. \textit{American Geophysical Union Fall Meeting}, New Orleans, LA, U.S.A.