\section*{OUTREACH \& PUBLIC SERVICE}

\subsection*{\textbf{Montshire Museum of Science} \hfill 2022\ongoing}
\subline{Guest Scientist}
\begin{itemize}
\item Lead and assist educational activities within the museum.
\item Explain Earth and space science concepts to pre-K through adult audiences.
\item Develop programming focused on planetary science topics.
\end{itemize}

\subsection*{\textbf{Santa Cruz Museum of Natural History} \hfill 2018 – 2022}
\subline{Volunteer Scientist}
\begin{itemize}
	\item Created educational content and hosted activities at monthly museum events.
	\item Co-hosted monthly educational video streams covering geoscience topics. \\
	Link: \href{https://www.santacruzmuseum.org/category/rockin-pop-up/}{\emph{Rockin' Pop-Up} Archives}.
\end{itemize}

\subsection*{\textbf{Skype a Scientist} \hfill 2019\ongoing}
\subline{Volunteer Scientist}
\begin{itemize}
	\item Prepare educational content and host video calls with elementary and secondary school classrooms.
	\item Teach geoscience concepts and share stories about experiences as a scientist.
\end{itemize}

\lineitem[2019 -- 2020]{Geoscientists Encouraging Openness and Diversity in the Earth Sciences\\(GEODES)}
\subline{Graduate Student Leader}
\begin{itemize}
	\item A student-run group in the UCSC Earth \& Planetary Sciences Department.
	\item One of six graduate student leaders responsible for the operation and development of GEODES.
	\item Organized and implemented outreach events centered on promoting underrepresented groups in the geosciences and cultivating a culture of inclusivity within the department.
\end{itemize}

\subsection*{\textbf{Peary-MacMillan Arctic Museum} \hspace{15pt} Brunswick, ME, U.S.A. \hfill 2012 -- 2016}
\subline[2015 -- 2016]{Curatorial Intern}
\begin{itemize}
	\item Developed outreach programming and exhibit content.
	\item Supplemented undergraduate courses with lectures and discussions drawing on museum collections.
	\item Mentored and trained undergraduate student interns and employees.
\end{itemize}

\subline[2012 -- 2014]{Student Tour Guide}
\begin{itemize}
	\item Led museum tours for all age groups of museum exhibits and interactive collections.
\end{itemize}

\subsection*{\textbf{Museum of the Rockies} \hspace{15pt} Bozeman, MT, U.S.A. \hfill 2015}
\textit{Security Volunteer}
\begin{itemize}
	\item Answered visitors' questions and facilitated interpretive discussions about natural history exhibits.
\end{itemize}