\section*{ACADEMIC SERVICE \& EXPERIENCE}

\lineitem[2023\ongoing]{Interdisciplinary Earth Data Alliance 2 (IEDA\textsuperscript{2})}
\subline{Community Advisory Board, \normalfont Co-Chair}
\begin{itemize}
	\item Co-chair of primary community advising body for the NSF-funded \href{https://www.iedadata.org/}{IEDA$^2$} data facility.
	\item Guide approaches to promote and ensure access, preservation, and re-usability of Earth system data.
\end{itemize}

\lineitem{Departmental Service}
\subline{Department of Earth Sciences, Dartmouth}
Postdoc Representative for Faculty Search Committee (2 searches) \hfill 2023, 2024
\begin{itemize}
	\item Organized meetings with candidates and departmental postdocs.
	\item Compiled and presented quantitative and qualitative feedback to Search Committee.
\end{itemize}\vspace*{1ex}

Earth \& Planetary History Journal Club --- Organizer 	 \hfill	Spring 2022
\begin{itemize}
	\item Scheduled, coordinated, and oversaw multidisciplinary reading group.
\end{itemize}

\subline{Department of Earth \& Planetary Sciences, UCSC}
Whole Earth Seminar --- Organizer \hfill  Spring 2019
\begin{itemize}
	\item Coordinated departmental seminar series (one of two graduate student organizers)
	\item Contacted and scheduled speakers from diverse disciplines in Earth and planetary sciences.
\end{itemize}

\lineitem{Laboratory Research \& Management}
Analytical Experience:
	\begin{itemize} [label={}]
		\item \textit{Expert:} TIMS
		\item \textit{Proficient:} MC-ICP-MS, ICP-MS, SEM-EDS
		\item \textit{Limited:} IRMS, ICP-OES, XRF, XRD
	\end{itemize} 
\subline[\hfill 2016 -- 2021]{W.M. Keck Isotope Facility, UC Santa Cruz}
Under the advisorship of lab director Prof. Terry Blackburn, I was partially responsible for the operation and maintenance of this multi-user clean lab facility, including:
	\begin{itemize} 
	\item Maintenance and operation of mass spectrometers and wet chemistry labs.
	\item Training and supporting researchers in chemical and mass spectrometric methods.
	\item Preparation, measurement, and reporting of isotopic analyses of geologic and biomineral material for external contracts.
	\item Procurement and preparation of lab consumables.
	\end{itemize}

\lineitem{Academic Meetings}
\subline{American Astronomical Society}
\begin{tabular}{ll} 
	2023 & Chambliss Award Judge (best student poster presentation)
\end{tabular}

\subline{Meteoritical Society Annual Meeting}
\begin{tabular}{ll} 
	2022 & 	McKay Award Judge (best student oral presentation)
\end{tabular}

\subline{AGU Fall Meeting}
\begin{tabular}{ll} 
	2017 & 	Co-Chair/Co-Convener:~~Applications of Thermochronology to Understand Crustal Systems
\end{tabular}

\vspace{2ex}
\begin{hangparas}{5ex}{1}
	\textbf{Reviewer for:} \textit{Geochronology}, \textit{Geology}, \textit{Nature Communications}

	\vspace{2ex}
	\textbf{Society Affiliations:} Meteoritical Society, American Astronomical Society, Geochemical Society, National Association of Geoscience Teachers, Geological Society of America, American Geophysical Union.
\end{hangparas}